Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-18 main.tex
abstract

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  In this paper we uncover a close relation between combinatorial and
  syntactic proofs for first-order logic. Whereas syntactic proofs are
  formalized in some deductive proof system based on inference rules,
  a combinatorial proof is a ``syntax-free'' presentation of a proof
  that is independent from any set of inference rules. We show that
  the two proof representations are related via a deep inference
  decomposition theorem that establishes a certain kind of normal form
  of syntactic proofs. As a consequence, we obtain (i) a simple proof
  of the soundness and completeness of first-order combinatorial
  proofs, and (ii) a full completeness theorem: every combinatorial
  proof is the image of a syntactic proof.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
  In this paper we uncover a close relation between combinatorial and
  syntactic proofs for first-order logic. Whereas syntactic proofs are
  formalized in some deductive proof system based on inference rules,
  a combinatorial proof is a ``syntax-free'' presentation of a proof
  that is independent from any set of inference rules. We show that
  the two proof representations are related via a deep inference
  decomposition theorem that establishes a new kind of normal form
  of syntactic proofs. As a consequence, we obtain (i) a simple proof
  of the soundness and completeness of first-order combinatorial
  proofs, and (ii) a full completeness theorem: every combinatorial
  proof is the image of a syntactic proof.
\end{abstract}
